---
title: "api_token"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{api_token}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spotify.discovery)
```

**Required.** Users must call this function in order to obtain an access token object required for the `spotifyr` package. Without an access token, the user will be unable to engage with the package. 

To obtain an access token, the user must run `api_token()` to call on Spotify’s API. Once the function is called, the user should look at Spotify's Web API website | Spotify for Developers (https://developer.spotify.com/documentation/web-api) via their search engine and will need to go through the SpotifyAPI’s process to obtain an access token. 

Once the access token is obtained, the user will be able to interact with all functions of the `spotify-discovery` package

**Instruction to Create API Token**

Creating an API token may seem daunting, but actually is quite easy with proper instructions. 

1. First you find your Spotify username and password, or you can make a Spotify account for free. To fully use the package, it’d be best to listen to music for at least a week, so Spotify can create a Discover Weekly playlist. However, you can also just use our playlist functions for whatever playlist you like. 

2. After acquiring your Spotify username and password, go to the Spotify developer page. Here you will create your app and receive your unique Client ID and Client Secret. 

3. Now you can install our package using `install.package(“spotify-discovery”)`. Then create a data object that will be your access token to all of our functions. 

`access_token <- api_token(‘YOUR CLIENT ID’, ‘YOUR CLIENT SECRET’)`

Now whenever you utilize one of our functions, place your access token in the function parameter inputs. 

**Notes**

Please note, you must reload your access token every hour in order for it to be valid. 

If the token expires, user will be prompted with message "access key expires in one hour - to renew please rerun this function"

To rerun function input: `access_token <- api_token(‘YOUR CLIENT ID’, ‘YOUR CLIENT SECRET’)` into the console


