---
title: "Function_Descriptions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function_Descriptions}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spotify.discovery)
```

**shuffle_function(username, uri, access_token, ...):**

The purpose of this function is so when listeners do not know what songs
to play, they can have a shuffled playlist from their Spotify Discover
Weekly! Users can provide their spotify username, URI, access token they
have created, and as well as any information they want to learn about
the songs. As of right now, the function outputs a dataframe with three
columns: "track.name", "track.album.name", and "track.preview_url".
These are only the defaults and if the user wants other information
about the songs such as music metrics, they can look at the options
provided below and add it as a parameter. Similarly, if you don't want
one of the default options, you can add "-"(parameter name).

The full list of options is:

-   "playlist_id"

-   "playlist_name"

-   "playlist_img"

-   "playlist_owner_name"

-   "playlist_owner_id"

-   "danceability"

-   "energy"

-   "key"

-   "loudness"

-   "mode"

-   "speechiness"

-   "acousticness"

-   "instrumentalness"

-   "liveness"

-   "valence"

-   "tempo"

-   "track.id"

-   "analysis_url"

-   "time_signature"

-   "added_at"

-   "is_local"

-   "primary_color"

-   "added_by.href"

-   "added_by.id"

-   "added_by.type"

-   "added_by.uri"

-   "added_by.external_urls.spotify"

-   "track.artists"

-   "track.available_markets"

-   "track.disc_number"

-   "track.duration_ms"

-   "track.episode"

-   "track.explicit"

-   "track.href"

-   "track.is_local"

-   "track.name"

-   "track.popularity"

-   "track.preview_url"

-   "track.track"

-   "track.track_number"

-   "track.type"

-   "track.uri"

-   "track.album.album_group"

-   "track.album.album_type"

-   "track.album.artists"

-   "track.album.available_markets"

-   "track.album.href"

-   "track.album.id"

-   "track.album.images"

-   "track.album.name"

-   "track.album.release_date"

-   "track.album.release_date_precision"

-   "track.album.total_tracks"

-   "track.album.type"

-   "track.album.uri"

-   "track.album.external_urls.spotify"

-   "track.external_ids.isrc"

-   "track.external_urls.spotify"

-   "video_thumbnail.url"

-   "key_name"

-   "mode_name"

-   "key_mode"

`shuffled_playlist('spotify', c('37i9dQZEVXbLRQDuF5jeBp'), access_token)`

```{r, echo = FALSE}
shuffled_playlist(test = TRUE) |>
  head(n=10)
```

**max_metric_summary(username, uri, access_token, max_or_min, ...)** :

User can provide a playlist via the get_playlist_audio_features()
function from the spotifyr package to produce a dataframe that includes
all audio metrics documented by spotify. The user may identify which
music metric to measure (Danceability, tempo, duration, etc.) and run
this function to produce a dataframe that documents the music metric,
the numeric value of the audio feature, and the title of the song
associated with that maximum value. This function works in conjunction
with the **min_metric_summary** function.

`max_metric_summary('spotify', c('37i9dQZEVXbLRQDuF5jeBp'), access_token)`

```{r, echo = FALSE}
max_metrics_summary(test = TRUE) |>
  head(n=10)
```

**min_metric_summary(username, uri, access_token, max_or_min, ...)** :

User can provide a playlist via the get_playlist_audio_features()
function from the spotifyr package to produce a dataframe that includes
all audio metrics documented by spotify. The user may identify which
music metric to measure (Danceability, tempo, duration, etc.) and run
this function to produce a dataframe that documents the music metric,
the numeric value of the audio feature, and the title of the song
associated with that minimum value. This function works in conjunction
with the **max_metric_summary** function. 

`min_metric_summary('spotify', c('37i9dQZEVXbLRQDuF5jeBp'), access_token)`

```{r, echo = FALSE}
min_metrics_summary(test = TRUE)
```

**genre_recommendations(uri, access_token)**:

User can provide a playlist and access token and it returns data frame
columns that represent the genre, and the rows represent the artist
name. The data frame shows similar artists and their genre based on the
user's inputted artist genre. Note: you may see the same artist you
inputted in the dataframe. This is because the artist you inputted is
already in the top 20 artists of that genre. You will still have 19 new
artists to listen to.

`genre_recommendations('spotify', c('37i9dQZEVXbLRQDuF5jeBp'), access_token)`

```{r, echo=FALSE}
genre_recommendations(test = TRUE) |>
  head(n=10)
```

**playlist_averages(username, uri, access_token, ...)**:

User can provide a playlist and access token and it returns a data frame
that shows the averages of the music metrics. The defaults for this are
'danceability', 'energy', 'speechiness', 'acousticness',
'instrumentalness', 'liveness', 'valence', 'tempo', and 'loudness'. The
user can add the metrics 'key', 'time_signature', 'track.duration_ms',
'track.popularity' using the "..." feature. Similarly, if you don't want
one of the default metrics, you can use "-(music metric)"

`playlist_averages('spotify', c('37i9dQZEVXbLRQDuF5jeBp'), access_token)`

```{r, echo=FALSE}
playlist_averages(test = TRUE) |>
  head(n=10)
```

**genre_playlist_recommendations(playlist, access_token)**

Users can provide a playlist URI and then receive 20 artist
recommendations based on the artist's genre in the playlist. Takes the
playlist URI and access token as input, and outputs a dataframe.

**Note:** You may see the same artist you inputted in the dataframe.
This is because the artist you inputted is already in the top 20 artists
of that genre. You will still have 19 new artists to listen to.

`genre_playlist_recommendations('37i9dQZF1EIVoBl2iylPUR', access_token)`

```{r, echo=FALSE}
genre_playlist_recommendations(test = TRUE) |>
  head(n=10)
```

**ranking_function(playlist, access_token, sort_by="track.name")**

Users can re-order their playlists based on an element of their choosing
in ascending order as the default, with the given constraint that it has
to be within a column provided by the get_playlist_tracks() function in
the spotifyr package since it was the function used to build
ranking_function().

The columns users can rank by are include:

-   "added_at"
-   "is_local"
-   "added_by.href"
-   "added_by.id"
-   "added_by.type"
-   "added_by.uri"
-   "added_by.external_urls.spotify"
-   "track.artists"
-   "track.available_markets"
-   "track.disc_number"
-   "track.duration_ms"
-   "track.episode"
-   "track.explicit"
-   "track.href"
-   "track.id"
-   "track.is_local"
-   "track.name"
-   "track.popularity"
-   "track.preview_url"
-   "track.track"
-   "track.track_number"
-   "track.type"
-   "track.uri"
-   "track.album.album_group"
-   "track.album.album_type"
-   "track.album.available_markets"
-   "track.album.href"
-   "track.album.id"
-   "track.album.name"
-   "track.album.release_date"
-   "track.album.release_date_precision"
-   "track.album.total_tracks"
-   "track.album.type"
-   "track.album.uri"
-   "track.album.external_urls.spotify"
-   "track.external_ids.isrc"
-   "track.external_urls.spotify"
-   "video_thumbnail.url"

**Note:** There are some columns such as "track.album.images" that are
dataframes within the dataframe, so we recommend you avoid those since
they will cause an error since the function currently can't index within
them, and you will be set back to the default of "track.name" if you try
to use these elements. There are also columns full of NA values that if
you try to rank them, it will not change the output of the dataframe.

**Note:** While you can technically you can rank by
"video_thumbnail.url", it will not provide you with a useful ordered
list so make sure you pay attention to what you sort by.

`ranking_function('37i9dQZF1EIVoBl2iylPUR', access_token, sort_by = 'track.duration_ms', order = 'ascending')`

```{r, echo=FALSE}
ranking_function(test = TRUE) |>
  head(n=10)
```
